---
title: "Rchamp"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rchamp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# How to get started. 

Right now, the package is being developed so use the following code to install the package. 

```{r setup, warning=FALSE,message=FALSE,error=FALSE}
devtools::install_github('mowgl-i/Rchamp@Development')
library(Rchamp)
```



## Twitch clip id

You'll want to have a slug/clip id to start with. 

This is the url a twitch clip : https://clips.twitch.tv/GracefulIntelligentKathyMikeHogu-uIO9Kd0g_KDqb4mQ

The slug/id can be found after the last shash : GracefulIntelligentKathyMikeHogu-uIO9Kd0g_KDqb4mQ

You will use this slug in the `get_clip_data()` and `get_clip_chat()` functions like so... `get_clip_data('slug')`


This will return

Messages as a list
Users as a list
Full data as list
Dataframe containing messages and Unsers

```{r}

get_clip_chat('GracefulIntelligentKathyMikeHogu-uIO9Kd0g_KDqb4mQ')
```

```{r}
head(chat_dataframe)

```

